### 2022-03-04 paper/localpsf.tex
editing kernel entries section

In detail, we form the approximation $\widetilde{\Phi}(y,x) \approx \Phi(y,x)$ as follows:

@@

r^d \log r & d=2,4,6,\dots

@@

In detail, define 
\begin{equation*}
\widehat{x_i} := x_i - x \qquad \text{and} \qquad \widehat{y_i} := y_i - y.
\end{equation*}
and let
\begin{equation*}
\widehat{B} = \begin{bmatrix}
\widehat{B}_{xx} & \widehat{B}_{xy} \\
\widehat{B}_{yx} & \widehat{B}_{xx}
\end{bmatrix}, \qquad \widehat{w} = \begin{bmatrix}\widehat{w}_x \\ \widehat{w}_y\end{bmatrix}, \qquad \widehat{f} = \begin{bmatrix}
\widehat{f}_x \\ \widehat{f}_y
\end{bmatrix},
\end{equation*}
be a $2k \times 2k$ block matrix and $2k \times 1$ block vectors, respectively, with the block entries of $\widehat{B}$ be given by
\begin{align*}
\left(\widehat{B}_{xx}\right)_{ij} = b\left(\|\widehat{x}_i - \widehat{x}_j\|\right), &\qquad
\left(\widehat{B}_{xy}\right)_{ij} = b\left(\|\widehat{x}_i - \widehat{y}_j\|\right), \\
\left(\widehat{B}_{yx}\right)_{ij} = b\left(\|\widehat{y}_i - \widehat{x}_j\|\right), &\qquad \left(\widehat{B}_{yy}\right)_{ij} = b\left(\|\widehat{y}_i - \widehat{y}_j\|\right),
\end{align*}
for $i,j=1,\dots,k$. We approximate $\Phi(y,x)$ as follows:
\begin{equation}
\widetilde{\Phi}(y,x) := \sum_{i=1}^k \left(w_x\right)_i~ b\left(\|\widehat{x}_i\|\right) + \sum_{i=1}^k \left(w_y\right)_i~ b\left(\|\widehat{y}_i\|\right),
\end{equation}
where $\widehat{w}$ is the solution of the following regularized least-squares problem,
\begin{equation*}
\min_{\widehat{w}} \frac{1}{2}\|\widehat{B} \widehat{w} - \widehat{f}\|^2 + \frac{\alpha}{2}\|\widehat{w}\|^2,
\end{equation*}
for a small regularization parameter $\alpha$. 
We solve the regularized least squares problem by QR factorization of the block $4k \times 2k$ matrix $\begin{bmatrix}\widehat{B} & I\end{bmatrix}^T$. We regularize the problem because of numerical issues that arise if there are points $\widehat{x}_i$ and $\widehat{y}_j$ in the interpolation that are equal or nearly equal, a situation that arises often in practice. 
%Indeed, situations where $\widehat{x}_i = \widehat{y}_j$ are inevitable when a regular grid is used to discretize the problem. 
In this case, $\widehat{B}$ is (nearly) singular, so it is ill-advised to solve the un-regularized interpolation system $\widehat{B} \widehat{w} = \widehat{f}$.

>>>>

In detail, we form $\widetilde{\Phi}(y,x) \approx \Phi(y,x)$ as follows:

@@

r^d \log r, & d=2,4,6,\dots

@@

In detail, define 
\begin{equation*}
\widehat{x_i} := x_i - x \qquad \text{and} \qquad \widehat{y_i} := y_i - y.
\end{equation*}
and let
\begin{equation*}
\widehat{B} = \begin{bmatrix}
\widehat{B}_{xx} & \widehat{B}_{xy} \\
\widehat{B}_{yx} & \widehat{B}_{xx}
\end{bmatrix}, \qquad \widehat{w} = \begin{bmatrix}\widehat{w}_x \\ \widehat{w}_y\end{bmatrix}, \qquad \widehat{f} = \begin{bmatrix}
\widehat{f}_x \\ \widehat{f}_y
\end{bmatrix},
\end{equation*}
be a $2k \times 2k$ block matrix and $2k \times 1$ block vectors, respectively, with the block entries of $\widehat{B}$ given by
\begin{align*}
\left(\widehat{B}_{xx}\right)_{ij} = b\left(\|\widehat{x}_i - \widehat{x}_j\|\right), &\qquad
\left(\widehat{B}_{xy}\right)_{ij} = b\left(\|\widehat{x}_i - \widehat{y}_j\|\right), \\
\left(\widehat{B}_{yx}\right)_{ij} = b\left(\|\widehat{y}_i - \widehat{x}_j\|\right), &\qquad \left(\widehat{B}_{yy}\right)_{ij} = b\left(\|\widehat{y}_i - \widehat{y}_j\|\right),
\end{align*}
for $i,j=1,\dots,k$. We approximate $\Phi(y,x)$ as follows:
\begin{equation}
\widetilde{\Phi}(y,x) := \sum_{i=1}^k \left(w_x\right)_i~ b\left(\|\widehat{x}_i\|\right) + \sum_{i=1}^k \left(w_y\right)_i~ b\left(\|\widehat{y}_i\|\right),
\end{equation}
where $\widehat{w}$ is the solution of the following regularized least-squares problem,
\begin{equation*}
\min_{\widehat{w}} \frac{1}{2}\|\widehat{B} \widehat{w} - \widehat{f}\|^2 + \frac{\alpha}{2}\|\widehat{w}\|^2,
\end{equation*}
for a small regularization parameter $\alpha$. 
We solve the regularized least squares problem by QR factorization of the block $4k \times 2k$ matrix $\begin{bmatrix}\widehat{B} & I\end{bmatrix}^T$. We regularize the problem because of numerical issues that arise if there are points $\widehat{x}_i$ and $\widehat{y}_j$ in the interpolation that are equal or nearly equal, a situation that arises often in practice. 
%Indeed, situations where $\widehat{x}_i = \widehat{y}_j$ are inevitable when a regular grid is used to discretize the problem. 
In this case, $\widehat{B}$ is (nearly) singular, so it is ill-advised to solve the un-regularized interpolation system $\widehat{B} \widehat{w} = \widehat{f}$.
